\section{Executive Summary(Abstract)}
The purpose of this report is to examine, expand and define the organizations current 
dependency on non-EU technology, evaluate the key risks associated with this direction, analyse
and propose EU alternatives. The goal is to identify and map a road to digital Sovereignty.

The current political climate is quite inhospitable and it has become apparent that 
world leaders make drastic, snap decisions that brings large implication to 
the technological landscape, where big tech can be leveraged as political weapons,
thus inherently changing the risk of reliance on such servies. Therefore companies, with suchs 
reliances, risks getting caught in the crossfire.  

Services where there is a heavy reliance, from companies such a \textit{Microsoft}, 
which hosts Azure \text{Active directory (AD)}, used for identity management, \textit{SharePoint} and \textit{OneDrive}, 
which Lifeline Health Technologies(LHT) uses as a file sharing service, could suddenly
become unavailable. 

A loss of this service, which would be tantamount to loss of many years of technological IPs 
and achievements which could lead to unquantifiable damage to the company. 
Therefore, in this inclememt weather, a EU alternative for these servises, is quintessential. % for a cloud based
%backup plan, along with a, yet to be implemented, physical backup. 

The main findings of this report is an overreliance on:
\begin{itemize}
    \item Microsoft Azure Services, where cloud hosting is indeterminate and 
    jurisdictional expose is somewhat vague. Thus EU laws may be hard to apply.
    \item Process and regulatory mismatches - Data is easily given up to 3rd party cloud services 
    or foreign governments, without regard for compliance (EU MDR)
    \item A thorough documentation is needed of other cloud solutions, specifically regarding SaaS tools.
\end{itemize}

Some of the main risks include:
\begin{itemize}
    \item Overreliance on providers like microsoft Azure services.
    \item Unsupported operating systems such as Windows Server '12R2, SQL 2016, windows 7 and XP.
    \item Unmainted local VM's, tightly coupled to on-prem hardware og dongles.  
    \item Unmainted network equipment.
    \item Poor physical access control.  
\end{itemize}


Examples for some EU-alternatives :
\begin{itemize}
    \item Univention - German based software for identity \& access management. A self hosted AD, requiring a virtual machine. 
    Can then handle all authentication, along with other features such as single sign-on(SSO) and multifactor authentication (MFA)
    \item Scaleway - A French based cloud provider, capable of hosting VM's for infrastructre purposes.
    \item KeyCloak - B2C IAM, which can be self hosted. Supporting OAuth2 and OpenID.
\end{itemize}

 
\subsection{Overall Conclusion}
This report supports the conclusion that an entirely new system, is recommended to be built
up in parallel, to remove the heavy reliance on non-EU service providers. A gradual transition 
is adviced, but that is not in the scope of the report.

% \begin{itemize}
%     \item current orgs dependency on non-EU technology
%     \item key risks
%     \item recommended EU alternatives
%     \item roadmap
% \end{itemize}


%%keep it one page max!

% add links/footnotes senere
% https://www.univention.com/
% https://www.scaleway.com/en/